The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-09-17 dit-paper_ieee.tex
removed a whitespace line
small things

\begin{abstract}
	Sensitivity analysis for real-time systems provides efficient methods to determine feasibility
	conditions in the case of small changes in task parameters, such as
	different WCET values when porting a system to a different platform. The C-space describes the set of execution
	times for which a system is feasible, which allows system designers to quickly
	find the best platform for a given task set. This paper extends previous works
	to generalize the description of the C-space for Earliest Deadline First
	scheduling to systems with initial task offsets. The feasibility gain offered
	by offsets is then expressed as the volume ratio between the C-space of an
	asynchronous system and its corresponding synchronous system. The problem
	requires solving multiple similar instances of the Chinese Remainder Problem,
	for which an algorithm efficient in this context is provided.
\end{abstract}

@@

	In Section~\ref{sct:asyncCspace}, we show how to describe the C-space of an asynchronous
	system based on the demand bound function test. Then we show why applying this
	test on the interval starting at $t_d$
	and spanning an hyperperiod when $t_d$ exists is sufficient. A
	numerical example is also given.

@@

	\subsection{Model}
		We consider a discrete timeline and tasks systems $\tau$ comprised of periodic
		tasks with constrained deadlines on uniprocessor platforms. Each task
		$\tau_i$ is represented by a tuple $(O_i, C_i, D_i, T_i)$ where $O_i$ is the offset value,
		$C_i$ the WCET, $D_i$ the relative deadline and $T_i$ the period.
		The constrained deadline property implies that $\forall i,\; D_i \leq T_i$. In
		the following, we differentiate between \emph{synchronous systems} (where $O_i
		= 0 \; \forall i$) and \emph{asynchronous systems} (which are not synchronous).

@@

		\begin{definition}
			The \textbf{demand-bound function (DBF)}
			defined for a task set $\tau$ in a time interval $[t_1, t_2]$ and denoted $\dbf{t_1, t_2}$, is
			equal to the maximal cumulated execution time of jobs of $\tau$ contained in the
			closed interval $[t_1, t_2]$.
		\end{definition}

@@

		This system is guaranteed to have at least one solution modulo $H$ for given
		values of $a_i$ if the following condition is respected:

		%Review 3 : use ref to justify this formula
		%TODO : change format so that the equation number is displayed correctly

		\begin{equation}
			a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i, T_j)) \; \forall i,j
		\end{equation}
		which means that there could be systems with no FPDIT.
		We now present an example of such a system.\\

@@

		The description we presented in Section \ref{sct:cspaceDescr} based on \cite{baruah1999generalized} was general, and
		is thus still relevant. Therefore the C-space is still accurately described by
		the following infinite number of constraints:

		\begin{equation}
			\sum_{i=1}^{n} n_i(t_1, t_2)
			\, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
		\end{equation}

		However, the method used in the synchronous case to remove redundancy does not
		apply here. A more general approach is presented in the following section.

>>>>

\begin{abstract}
	Sensitivity analysis for real-time systems provides efficient methods to determine feasibility
	conditions in the case of small changes in task parameters, such as
	different WCET values when porting a system to a different platform. The \mbox{C-space} describes the set of execution
	times for which a system is feasible, which allows system designers to quickly
	find the best platform for a given task set. This paper extends previous works
	to generalize the description of the C-space for Earliest Deadline First
	scheduling to systems with initial task offsets. The feasibility gain offered
	by offsets is then expressed as the volume ratio between the C-space of an
	asynchronous system and its corresponding synchronous system. The problem
	requires solving multiple similar instances of the Chinese Remainder Problem,
	for which an algorithm efficient in this context is provided.
\end{abstract}

@@

	In Section~\ref{sct:asyncCspace}, we show how to describe the C-space of an asynchronous
	system based on the demand bound function test. Then we show why applying this
	test on the interval starting at $t_d$
	and spanning an hyperperiod is sufficient when $t_d$ exists. A
	numerical example is also given.

@@

	\subsection{Model}
		We consider a discrete timeline and tasks systems $\tau$ comprised of periodic
		tasks with constrained deadlines on uniprocessor platforms. Each task
		$\tau_i$ is represented by a tuple $(O_i, C_i, D_i, T_i)$ where $O_i$ is the offset value,
		$C_i$ the WCET, $D_i$ the relative deadline and $T_i$ the period, which is the exact time between two consecutive arrivals.
		The constrained deadline property implies that $D_i \leq T_i \; \forall i$. In
		the following, we differentiate between \emph{synchronous systems} (where $O_i
		= 0 \; \forall i$) and \emph{asynchronous systems} (which are not synchronous).

@@

		\begin{definition}
			The \textbf{demand-bound function (DBF)}
			defined for a task set $\tau$ in a time interval $[t_1, t_2]$ and denoted $\dbf{t_1, t_2}$, is
			equal to the maximum cumulated execution time of jobs of $\tau$ contained in the
			closed interval $[t_1, t_2]$.
		\end{definition}

@@

		This system is guaranteed to have at least one solution modulo $H$ for given
		values of $a_i$ if the following condition is respected:
		%Review 3 : use ref to justify this formula
		\begin{equation}
			a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i, T_j)) \; \forall i,j
		\end{equation}
		which means that there could be systems with no FPDIT.
		We now present an example of such a system.\\

@@

		The description we presented in Section \ref{sct:cspaceDescr} based on \cite{baruah1999generalized} was general, and
		is thus still relevant. Therefore the C-space is still accurately described by
		the following infinite number of constraints:
		\begin{equation}
			\sum_{i=1}^{n} n_i(t_1, t_2)
			\, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
		\end{equation}
		However, the method used in the synchronous case to remove redundancy does not
		apply here. A more general approach is presented in the following section.
